---
title: Unsolicited advice on surviving a PhD
date: '2022-05-09'
categories:
  - Academia
  - Explainer
subtitle: 'Reflections from my own journey'
description: ''
date-modified: '2022-05-09'
draft: true
---

```{r, label='setup-options', include=FALSE}
knitr::opts_chunk$set(
  eval = TRUE, # eval code chunks
  echo = FALSE, # include source code
  #fig.width = 6, # set figure dims
  #fig.height = 6
  fig.align = 'center',
  warning = FALSE, # exclude warnings
  message = FALSE, # exclude messages
  error = FALSE # exclude errors
)
```

So it's been a hot minute since my [last post](../../../../post/progress-in-open-research), but I have since passed my *viva* with minor corrections, and have since had said thesis corrections approved, and so I've successfully completed my PhD!

```{r}
knitr::include_graphics(
  'https://media.giphy.com/media/3ohuPh9eyi4Av2DlM4/giphy.gif'
)
```

<!-- insert happy celebrations here -->
<!-- also update link to prior paper post -->

On this occasion, I think I'll skip my usual attempt at a lay-friendly summary of my work, as my [prior post](../../../../post/first-publication) covers the first results chapter, and I'll write up the last chapters work when we publish the next paper!
Instead, this seemed like a good time to think about my PhD journey, mostly to force myself to reflect, but who knows, maybe some lost soul will find my rambling useful.

Before that though, I'll offer some thoughts on what advice I might have benefited from at the start of this process

# Learn to code!

So anyone who knows me in a professional capacity will be unsurprised by this, but my main thought is: **learn to code!**

Seriously.
It really doesn't matter what your particular field is, if you're doing a vaguely science-based PhD and you don't already know R or Python, now is the time to learn.
It's far too useful as a skill to not spend some time on, and there's a decent chance you'll find someone in your lab who may be able to help you with this.
Even if you don't though, there's plenty of great free learning resources online, both in written and video formats.

I went into my PhD with an interest in programming, but no experience with it, but my supervisor was very supportive of me learning, despite not having the skill herself.
This was partly because I'm a nerd, but also because I foresaw that I might be working with datasets that would be unwieldy in something like Excel or SPSS, but even if this isn't true for you, I'd still encourage it.
It will make you more efficient, versatile and employable, and in the end I suspect the skill will save you more time than you spend learning in the first instance.
And you're work will be much more reproducible, but I got into more detail on why all scientists should learn to code [in another post](https://oskor.netlify.app/post/reproducible-data-analysis/), so give that a read if you're unconvinced.

# Tools for thesis writing

What I didn't expect is to end up writing my whole thesis in [R Markdown](https://rmarkdown.rstudio.com/), but I'd suggest you consider giving it a go.
It doesn't have to be R Markdown specifically (maybe try the newer [Quarto](https://quarto.org/), it seems pretty neat from my brief experimentation), any plain text format that works for you would be a huge improvement over Word.

This will allow your writing to be reproducible as well, but more pragmatically it will save you loads of time!
If you've ever written long-form content, like a dissertation, in Word, you'll know how much of a hassel sorting references, figure/table/section/page numbering, table of contents/figures/tables/abbreviations can be, and how much time it can take up, especially right before a deadline.

Using sometime like R Markdown allows the computer to sort all of these things automatically.
Need to move a whole section somewhere else?
In Word, this is a nightmare, but not so with R Markdown.
I used the lovely [bookdown](https://bookdown.org/yihui/bookdown/) and [thesisdown](https://github.com/ismayc/thesisdown) packages specifically, and they worked wonderfully.


